---
title: "P8105_hw5_qs2200"
author: "Qi Shao"
date: "11/6/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
```

## Problem 1

### Dataframe contains file names
```{r problem 1.1}
zip_file = tibble(file_name = list.files("./data/problem1"))
zip_file
```

### Read data
```{r problem 1.2, message = F}
read_file = function(x){
  
  x = str_c("./data/problem1/", x)
  read_csv(x)
  
}

zip_file = 
  zip_file %>%
  mutate(data = map(zip_file$file_name, read_file))
```

### Tidy data
```{r problem 1.3}
zip_file = 
  unnest(zip_file) %>%
  separate(file_name, into =c("arm", "id"), sep = "_") %>%
  separate(id, into =c("id", "other"), sep = ".csv") %>%
  gather(key = week, value = observation, week_1:week_8) %>%
  separate(week, into = c("rm", "week"), sep = "_") %>%
  select(-other, -rm )
```

### Make a spaghetti plot
```{r problem 1.4}
zip_file %>%
  mutate(week = as.numeric(week))%>%
  ggplot(aes(x = week, y = observation, color = id)) +
  geom_line()+
  facet_grid(~arm)+
  viridis::scale_color_viridis(
    name = "ID", 
    discrete = TRUE
  )+
  theme_minimal() 
```

From this spaghetti plot, we can see that the observations of control arm remain stable during the 8 weeks, but in experimental arm, the value of observations rise obviously as time went on. So we can conclude that there is a association between experiment variable and observation.

## Problem 2

### Describe the raw data
```{r problem 2.1}
read_csv("./data/homicide-data.csv")
```


### Tidy and summarise the data
```{r problem 2.2}
homi_df = 
  read_csv("./data/homicide-data.csv") %>%
  mutate(city_state = str_c(city, ", ", state)) %>%
  group_by(city_state, disposition) %>%
  summarise(total= n()) %>%
  spread(key = disposition, value = total) %>%
  janitor::clean_names() %>%
  mutate(total_homi = rowSums(cbind(closed_by_arrest, closed_without_arrest, open_no_arrest), na.rm = T), unsolve_homi = rowSums(cbind(closed_without_arrest, open_no_arrest), na.rm = T)) %>%
  select(- closed_by_arrest, - closed_without_arrest, -open_no_arrest)
```

### Estimate the proportion of unsolved homicides in Baltimore
```{r problem 2.3}



```